Variants on the Flight and Maintenance Planning problem

### 2018-07-13 latex/notes/complexite/FMP_variants.tex
updated notes on complexity

    Let $J = {1, ..., n}$ be the set of tasks to be assigned and $E = {1, ..., m}$ the set of employees. Each task $j \in J$ has a duration $u_j$ , a start time $s_j$ and a finish time $f_j$ = $s_j + u_j$ . Each employee e has a set of tasks $J_e \in J$ that he/she can perform. Similarly, for each task $j$, a set $E_j \in E$ exists, which contains all employees that can perform task $j$. Both $T_e$ and $E_j$ are defined based on qualifications, time windows of tasks and availabilities of employees.

@@

    For each employee $e \in E$, we create an analogous resource $i \in I$ which we will use indistinctly.

    For each task $j \in J$, we create a $j \in J$ task in our problem with duration and minimal assignment time equal to $A^{min}_j = u_j$. Start times and finish times define the moment when the task is active: $\mathcal{T}_j = t \in \{s_j ... f_j\}$. The need of resources for each task will be constant $R_{j} = 1$. The number of resources working at any given time can $D_t = |\mathcal{J}_t|$ can be calculated. The relationship between tasks and employees is also equivalent: $\mathcal{O}_i = J_i$ and $\mathcal{I}_j = E_j$.

    The usage time for each resource by any task will be $H_j = 0$ and the remaining usage time after a maintenance is $H = 0$.
    For maintenances, we can just take them out of the equation completely. For this we just need to put: $E_{min} = E = M = N_t = 0$ and $Ret^{Init}_{i} = |\mathcal{T}| + 1$.

@@

    \begin{tabular}{ll}
        $\mathcal{T}$       & Planning horizon periods. \\
        $\mathcal{I}$       & Resources. \\
        $\mathcal{J}$       & tasks.  \\
        $\mathcal{T}_j$     &  time periods $t \in \mathcal{T}$ in which task $j$ is active. \\
        $\mathcal{J}_t$     &  tasks $j \in \mathcal{J}$ to be realized in period $t$. \\
        $\mathcal{I}_j$     &  resources $i \in \mathcal{I}$ that can be assigned to task $j$. \\
        $\mathcal{O}_i$     &  tasks $j \in \mathcal{J}$ for which resource $i$ can be used. \\
        $\mathcal{T}^{s}_t$ &  time periods $t' \in \mathcal{T}$ such that $t' \in \{ \max{\{1, t - M+1\}},  ..., {t}$\}. \\
    \end{tabular}

    \begin{tabular}{ll}
        $M_{min}$        & Minimum number of maintenances per resource in planning horizon. \\
        $M$              & Duration of maintenance. \\
        $E$              & Maximum elapsed time before assigning a maintenance. \\
        $E_{min}$        & Minimum elapsed time before assigning a maintenance. \\
        $R_{j}$          & Need of resources for task $j$. \\
        $H$              & remaining usage time after a maintenance. \\
        $D_t$            & number of resources to be assigned in total in period $t$. \\
        $A^min_j$        & minimum number of consecutive periods to assign any resource to task $j$. \\
        $Ret^{Init}_{i}$ & remaining elapsed time for resource $i$ at the start of the planning horizon. \\
    \end{tabular}

        \begin{tabular}{ll}
            $at^{init}_{it}$    &  =1 if resource $i \in I$ starts a mission assignment in period $t \in \mathcal{T}$, 0 otherwise. \\
        \end{tabular}

    The model would need to have constraints of minimum assignment. For this, we would have to implement a new variable for missions that would be similar to the one in maintenances (a 'start' of mission assignment) and then tie this new variable to the regular assignments.

        \begin{align}
            &  at^{init}_{it} \geq at_{it}
                & i \in \mathcal{I} \label{eq:min_maintenace2}\\
        \end{align}

>>>>

    Let $P = {1, ..., n}$ be the set of tasks to be assigned and $E = {1, ..., m}$ the set of employees. Each task $p \in P$ has a duration $u_p$ , a start time $s_p$ and a finish time $f_p$ = $s_p + u_p$ . Each employee $e$ has a set of tasks $P_e \in P$ that he/she can perform. Similarly, for each task $p$, a set $E_p \in E$ exists, which contains all employees that can perform task $p$. Both $T_e$ and $E_p$ are defined based on qualifications, time windows of tasks and availabilities of employees.

    The reference problem has the following characteristics.

    $\mathcal{P}_{ref}$:

    \begin{tabular}{ll}
        $\mathcal{E}$       & Employees. \\
        $\mathcal{P}$       & tasks.  \\
        $u_p$     			&  Duration of task $p$. \\
        $s_p$     			&  Starting times $p$. \\
        $f_p$     			&  finish time of task $p$. \\
        $S_e$     &  Set of tasks an employee $e$ can perform. \\
        $E_p$ &  Set of employees that can perform task $p$. \\
    \end{tabular}

@@

    % For each employee $e \in E$, we create an analogous resource $i \in I$ which we will use indistinctly.

    % For each task $j \in J$, we create a $j \in J$ task in our problem with duration and minimal assignment time equal to $A^{min}_j = u_j$. Start times and finish times define the moment when the task is active: $\mathcal{T}_j = t \in \{s_j ... f_j\}$. The need of resources for each task will be constant $R_{j} = 1$. The number of resources working at any given time can $D_t = |\mathcal{J}_t|$ can be calculated. The relationship between tasks and employees is also equivalent: $\mathcal{O}_i = J_i$ and $\mathcal{I}_j = E_j$.

    % The usage time for each resource by any task will be $H_j = 0$ and the remaining usage time after a maintenance is $H = 0$.
    % For maintenances, we can just take them out of the equation completely. For this we just need to put: $E_{min} = E = M = N_t = 0$ and $Ret^{Init}_{i} = |\mathcal{T}| + 1$.

    % An instance of our problem is the following:

    % \subsection{Notations}

    The FMP problem has the following characteristics.

    $\mathcal{P}_{FMP}$:

@@

    \begin{tabular}{l|l|l}
    	\textbf{FMP}    &  \textbf{Meaning} & \textbf{f(I)} \\ \hline
        $\mathcal{T}$    &  Planning horizon. & $\{\min_p({s_p}) ... \max_p({f_p})\}$ \\
        $\mathcal{I}$    &  Resources. & $ \mathcal{E}$ \\
        $\mathcal{J}$    &  Tasks.  & $ P$ \\
        $\mathcal{T}_j$  &  time periods in which task $j$ is active. & $t \in \{s_p ... f_p\}$ \\
        $\mathcal{J}_t$  &  tasks to be realized in period $t$. & $j | t \in \{s_p ... f_p\}$ \\
        $\mathcal{I}_j$  &  resources that can be assigned to task $j$. & $E_p$\\
        $\mathcal{O}_i$  &  tasks for which resource $i$ can be used. & $P_i$ \\
        $\mathcal{T}^{s}_t$ &  time periods $t' \in \mathcal{T}$ that control de maintenance starts. & $\{\}$ \\
    \end{tabular}

    \textbf{Parameters}

    \begin{tabular}{l|l|l}
    	\textbf{FMP}    &  \textbf{Meaning} & \textbf{f(I)} \\ \hline
        $D_t$            & number of resources to be assigned in total in period $t$ & $|\mathcal{J}_t|$\\
        $A^{min}_j$      & minimum number of consecutive periods for task $j$. & $u_p$ \\
        $Ret^{Init}_{i}$ & remaining elapsed time for resource $i$ at the start. & $|\mathcal{T}| + 1$ \\
        $R_{j}$          & Need of resources for task $j$ & $1$ \\
        $H_j$             & amount of resource time required by task $j$. & $ 0$ \\
        $M$               & maintenance duration in number of periods. & $ 0$ \\
        $E$               & remaining elapsed time after a maintenance. & $ 0$ \\
        $H$               & remaining usage time after a maintenance.& $ 0$ \\
        $N_t$             & number of resources in already-planned maintenances in period $t$ at the start. & $0$ \\
        $Rut^{Init}_{i}$  & remaining usage time for resource $i$ at the start of the planning horizon. & $ 0$ \\
        $Ret^{Init}_{sum}$& sum of remaining elapsed times at the start of the planning horizon. & $ 0$\\
        $Rut^{Init}_{sum}$& sum of remaining elapsed time at the start of the planning horizon. & $ 0$ \\
    \end{tabular}
